Incremental λ-Calculus in Cache-Transfer Style

### 2017-07-11 popl18/static-differentiation-soundness.tex
Differentiation soundness: incorporate crucial corollary
Most papers don't stop at fundamental properties but at their interesting
corollary.

We can state a soundness theorem for differentiation without
mentioning step-indexes. Instead of proving it directly, we must first
prove a more technical statement
(Lemma~\ref{lemma:fundamental-property}) that mentions step-indexes
explicitly.
%
\begin{theorem}[Soundness of differentiation in $\source$]
  \label{thm:sound-derive}
  If $\iectx$ is a valid change environment from base environment $\sectx_1$ to
  updated environment $\sectx_2$, that is $\vvcrel {\sectx_2} {} {\sectx_1}\iectx$,
  %
  and if $\sterm$ converges both in the base and updated environment, that is
  $\sneval{\sectx_1}\sterm{\sclosedvalue_1}$ and
  $\sneval{\sectx_2}\sterm{\sclosedvalue_2}$,
  %
  then $\iderive\sterm$ evaluates under the change environment~$\iectx$ to a valid
  change $\icloseddvalue$ between base result ${\sclosedvalue_1}$ and updated result
  ${\sclosedvalue_2}$, that is
  $\sneval\iectx{\iderive\sterm}{\icloseddvalue}$ and
  $\vvcrel{\sclosedvalue_2} {} {\sclosedvalue_1}
  \icloseddvalue$.
\end{theorem}

>>>>

We can state a soundness theorem for differentiation without
mentioning step-indexes. Instead of proving it directly, we must first
prove a more technical statement
(Lemma~\ref{lemma:fundamental-property}) that mentions step-indexes
explicitly.
%
\begin{theorem}[Soundness of differentiation in $\source$]
  \label{thm:sound-derive}
  If $\iectx$ is a valid change environment from base environment $\sectx_1$ to
  updated environment $\sectx_2$, that is $\vvcrel {\sectx_2} {} {\sectx_1}\iectx$,
  %
  and if $\sterm$ converges both in the base and updated environment, that is
  $\sneval{\sectx_1}\sterm{\sclosedvalue_1}$ and
  $\sneval{\sectx_2}\sterm{\sclosedvalue_2}$,
  %
  then $\iderive\sterm$ evaluates under the change environment~$\iectx$ to a valid
  change $\icloseddvalue$ between base result ${\sclosedvalue_1}$ and updated result
  ${\sclosedvalue_2}$, that is
  $\sneval\iectx{\iderive\sterm}{\icloseddvalue}$,
  $\vvcrel{\sclosedvalue_2} {} {\sclosedvalue_1}
  \icloseddvalue$ and
  $\sclosedvalue_1 \oplus \icloseddvalue = \sclosedvalue_2$.
\end{theorem}
